Safe Memory Regions for Big Data Processing

### 2016-10-20 paper/type-inference.tex
minor fix to proofs

\begin{lemma}
  \label{lemma:completely-bound}
Let $C = \consOf{q}$.
Every region variable occurring in $\satC$ is bound to some region constant in $\satC$.
\end{lemma}

The set $\satC$ makes it easy to identify a solution $\thesoln$ (if one exists), as below.
\begin{itemize}
\item For any predicate variable $\varphi$, $\thesolnP(\varphi)$ is defined
to be $\conj \{ \pi_1 \outlives \pi_2 \;|\; \pi_1, \pi_2 \in \regionConstants, \isvalid{\varphi}{\pi_1 \outlives \pi_2} \in \saturate{C} \}$.
\item For any region variable $\rho$, we define $\thesolnR(\rho)$ to be any element of the
set $\{ \pi \in \regionConstants \:|\; \isvalid{\ell}{\rho = \pi} \in \saturate{C} \}$.
\end{itemize}

@@

\[
\solveCon{C} = 
\begin{cases}
\textsc{Some} (\thesoln) & \textrm{if $\groundC$ is valid and $\thesoln$ satisfies $\rhoC$} \\
\textsc{None} & \textrm{otherwise}
\end{cases}
\]

>>>>

%\begin{lemma}
%  \label{lemma:completely-bound}
%Let $C = \consOf{q}$.
%Every region variable occurring in $\satC$ is bound to some region constant in $\satC$.
%\end{lemma}

The set $\satC$ makes it easy to identify a solution $\thesoln$ (if one exists), as below.
\begin{itemize}
\item For any predicate variable $\varphi$, $\thesolnP(\varphi)$ is defined
to be $\conj \{ \pi_1 \outlives \pi_2 \;|\; \pi_1, \pi_2 \in \regionConstants, \isvalid{\varphi}{\pi_1 \outlives \pi_2} \in \saturate{C} \}$.
\item For any region variable $\rho$, we define $\thesolnR(\rho)$ to be any element of the
set $\{ \pi \in \regionConstants \:|\; \isvalid{\ell}{\rho = \pi} \in \saturate{C} \}$,
if this set is non-empty. If this set is empty for any $\rho$, $\thesoln$ is undefined.
\end{itemize}

@@

\[
\solveCon{C} = 
\begin{cases}
\textsc{Some} (\thesoln) & \textrm{if $\groundC$ is valid and $\thesoln$ is defined and satisfies $\rhoC$} \\
\textsc{None} & \textrm{otherwise}
\end{cases}
\]
